Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-07-04 WRITEUP/ms.tex
more revisions to 5; fixed a compile error

% address the biggest MCC = molecular disk of \flower
%mm2 [This figure would be better with a color bar rather than the
%prominent stars at the bottom...]
\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{\figpath/cloud-mass_fgas.pdf}
\caption{Cloud mass and stellar-to-gas mass ratio of MCCs identified in the accreting phase of \flower with different $n_{\rm cut}$. The most massive structures
identified with a low $f_{\rm gas}$ correspond to the molecular disk/arms of \flower (see also \Fig{vv}).
%
Thus, these structures encompass a large amount of stellar mass that is already assembled in \flower. These disk/arm structures are excluded 
in the discussion of MCC dynamics in the remainder of this paper. 
\label{fig:stellarRatio16}}
\end{figure}

The most massive structures ($M_{\rm gas}>$10$^7$\,\Msun) correspond
to the molecular disk of the galaxy (see e.g., \Fig{MCC}), which is
identified as a single component at low $n_{\rm cut}$. This main disk
component
% mm2 occupy the top right   [left not right!]
          occupies the top left
corner of \Fig{stellarRatio16}, with a low gas mass fraction of $f_{\rm gas}< 5\%$. The velocity dispersion of such structure is dominated by bulk motions, as shown in \Fig{vv}, where we compare the velocity dispersions of MCCs resulting from bulk ($\sigma_{\rm bulk}$) versus non-thermal turbulent motions ($\sigma_{\rm NT}$) in the accreting and quiescent phases of \flower. The accreting phase of \flower displays a disturbed morphology, whereas the quiescent phase displays a disk-like morphology (\Fig{MCC}).
%
Excluding the structure corresponding to the molecular disk, the velocity dispersions of most MCCs in the accreting phase of \flower are dominated by turbulent motions. On the other hand, $\sigma_{\rm bulk}$ is at least comparable to $\sigma_{\rm NT}$ for almost half the MCCs in the quiescent disk-like phase.
%
For these reasons, the most massive MCCs are excluded in the discussion of the dynamics (\Sec{diss}), as they are dominated by large-scale shear; however, we include them in the scaling relation plots (\Fig{larsons_single} and \Fig{alpha16-28}), as would be done so for an observational study.

@@

\begin{figure}
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss16-28-veldisp.pdf}
\caption{Gas velocity dispersions resulting from bulk versus turbulent motions for molecular structures 
identified across all $n_{\rm cut}$, as shown using the same color-coding as \Fig{stellarRatio16}.
%
Top and bottom panels show structures identified in the accreting phase and the quiescent phase, respectively.
The accreting phase of \flower displays a more disturbed morphology compared to the quiescent phase, which displays a disk-like morphology (see \Fig{MCC}).
%
The dashed black lines show a one-to-one mapping between the axes to facilitate comparison. 
%
Velocity dispersion from turbulent motions dominates over bulk motions for MCCs in the accreting phase, whereas 
$\sigma_{\rm bulk}$ is comparable to $\sigma_{\rm NT}$ for some MCCs in the quiescent disk-like phase.
\label{fig:vv}}
\vspace{0.5em}
\end{figure}

@@

\begin{figure*}
\centering
\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/3by2_clumpProp_ss16-ss22.png}
\caption{
Linewidth-size relation (top), $\alpha_{\rm vir}$-mass relation
(middle), and $\sigma_{\rm gas}^2/R$-$\Sigma_{\rm gas}$ relation (bottom) for
MCCs (star symbols) identified in the two most extreme evolutionary
stages of \flower\ --- accreting (left) and starburst (right). Star symbols are color-coded by density thresholds
$n_{\rm cut}$, as illustrated by the colorbar shown on the right.
Gas-only $\alpha_{\rm vir}$ (orange star symbols) is overplotted, and is of the same order of magnitude as $\alpha_{\rm vir, tot}$ for most MCCs
since they are gas-dominated (see \Fig{stellarRatio16}) \AP{I think the orange points makes the figure more messy, an alternative would to remove them and discuss the point in the text}. 
Stability of the biggest structures is strongly influenced by the stellar component, given their low $f_{\rm gas}$ (see \Fig{stellarRatio16} and \Sec{dist}).
The gray dotted lines shown in the bottom panels correspond to the various annotated external pressures needed in order for
the gas to be in equilibrium, see Equation~\ref{eqn:v0}.
Literature data are taken from \citet{Larson81a, Heyer04a, Rosolowsky05a, Bolatto08a, 
Swinbank11a, Leroy15a, Kauffmann17a}, % black dot = extragalactic GMCs in quiescent environments
MCCs in the starburst phrase have lower $\alpha_{\rm vir}$ than in the accreting phase.
and \citet{Kauffmann17b}.
\label{fig:larsons_single}}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[trim=0 0 0 0, clip, width=1.05\textwidth]{\figpath/3by2_clumpProp_allss}
\caption{Same as \Fig{larsons_single}, except star symbols are showing molecular gas structures identified across all evolutionary stages traced in our simulation, which are color-coded by the SFR of \flower in those stages (see colorbar on the right). Left panels show structures identified using a low density threshold of $n_{\rm cut}$\eq0.53\,\cc and the right panels show those identified using a high density threshold of $n_{\rm cut}$\eq18.96\,\cc.
The biggest MCCs identified at lowest density thresholds, occupying the top right corner of the top left panel, correspond to the molecular 
disk and arms of \flower, and are broken down into smaller MCCs at higher density thresholds (see top right panel). 
Notably less MCCs in the right panels owing to the fact that only few MCCs with neighboring cells reaching high H$_2$ densities of $n_{\rm cut}\simeq$19\,\cc.
The high velocity dispersion in \flower is largely driven by non-thermal pressure (see \Fig{vv}).
\label{fig:alpha16-28}}
\end{figure*}

Here, we focus on the MCC properties in the two most extreme evolutionary stages of \flower\ --- the accreting and starburst phases (see \Sec{sfh}). 
These properties are plotted in \Fig{larsons_single} together with observational results of nearby and $z$\,$\simeq$2 molecular structures for comparison.

During the accreting phase, MCCs in \flower\ are characterized by large velocity dispersions ($\sigma \simeq 100 {\rm km s}^{-1}$) and sizes ($R\simeq 100$\,pc). These values are comparable to those found in starburst galaxies, such as the nearby gas-rich galaxy M64 and the $z$\ssim2 starbursting disk galaxy SMM\,J2135-0102 \citep{Rosolowsky05a, Swinbank11a}, but are higher than those found in the Milky Way and extragalactic GMCs by an order of magnitude \citep{Heyer04a, Bolatto08a}.

% middle
While the virial parameter defined as Equation~\ref{eqn:alpha} is typically used in observational studies, as they are designed to probe structures that are composed of mainly molecular gas only, we calculate the virial parameter of MCCs including the influence from the stellar component (i.e., $\alpha_{\rm vir, tot}$ via Equation~\ref{eqn:alpha_tot}) given the high stellar-to-gas mass ratios of some molecular structures identified (see \Fig{stellarRatio16}).
% 
The biggest MCC identified at low $n_{\rm cut}$ and with the highest stellar-to-gas mass ratio ($\gtrsim$\,1; \Fig{stellarRatio16}) corresponds to the central main 
disk of \flower (see top panels of \Fig{MCC} and \Sec{distribution}). The large amount of stellar mass already assembled in \flower
explains the low {\em total} virial parameter seen in the middle left panel of \Fig{larsons_single}, where the stellar gravitational potential 
influences the overall stability. On the other hand, the MCCs in this phase are mostly stable, with 
virial parameter comparable to some of the molecular structures observed in the Milky Way but the former is more massive.

@@

If constant column density (Larson's third relation) is truly a fundamental properties of molecular clouds % or the roughly linear relationship between $\rho$ and $R$ of MCCs.
(i.e., if virialization is a universal property of molecular clouds with negligible surface pressure), 
one would expect a single point in the $\sigma_{\rm gas}^2/R$--$\Sigma$ relation at a given gas mass surface density $\Sigma$. 
The variation in $\sigma_{\rm gas}^2/R$ with $\Sigma$ seen here suggests that column density is not a fundamental properties of 
molecular clouds. Previous studies suggest that the observed mass-size relation of molecular clouds 
is solely a result of $\rho\propto M R^{-3}$ and may be an artifact of the limited range of 
column densities a specific molecular line tracer is sensitive to \citep[see e.g.,][]{Ballesteros02a, Ballesteros11a}.
%For instance, \citet{Ballesteros02a} show that the density
%of clouds ($\rho$) is independent of their size ($R$) when one properly extract these quantities in three-dimensional space instead of
%two-dimensional space; the latter is done in \obs.
%When they project the clouds into two-dimensional space and measure the densities and sizes of clouds for a given
%line tracer, they find $\rho \propto R^{-1}$, which is unsurprising since $N_H$ is just a constant.
%They therefore argue that the mass-size relation is simply a result of $\rho\propto M R^{-3}$
%observed in 2D-space at a fixed column density (cf. an actual physical relation of $M \propto R^{4/3}$ claimed in
%observational studies). % where $\rho$ would be proportional to $R^{-1/2}$
%% since $M$ would then scale as $R^{3}$ (ånd naturally display a linear relationship in $\log M - \log R$ plot).

@@

% Starburst
In the starburst phase, MCCs have velocity dispersion and sizes similar to those in the accreting phase; however, 
MCCs in the starburst phase span a wider range in gas surface density 
(bottom panels of \Fig{larsons_single}) and have lower virial parameters.
That is, MCCs in the starburst phase are more susceptible to collapse, as expected.
The gas surface density of MCCs in both accreting and starburst phases is higher than that in the solar neighborhood
of the Milky Way and the Large Magellanic Cloud (LMC), but comparable to those observed in starburst galaxies and the nearby 
ultra-luminous IR galaxies (ULIRGs) \citep{Boulares90a, Scoville91a, Weiss01a, Hughes10a, Leroy15a}.
% LMC: 0.01 g cm^-2
% M82: 0.1 g cm^-2
% Arp 220: 7-20 g cm^-2
%
% Due to a time delay between cloud collapse and \SF, we also compare the virial parameter of MCCs in the pre-starburst phase and post-starburst phase.
%\Fig{alphaEvol} shows that most MCCs in the pre-starburst phase have even lower virial parameter than in the starburst phase. On the other hand,
%the virial parameter of MCCs in the post-starburst phase is higher than in both the pre-starburst and the starburst phase.
%This is consistent with our physical intuition of gas instability leading to \SF.

>>>>

% address the biggest MCC = molecular disk of \flower
%mm2 [This and following figures would be better with the  color bar
%from Figure 7 rather than the prominent stars at the bottom...]
\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{\figpath/cloud-mass_fgas.pdf}
\caption{Cloud mass and stellar-to-gas mass ratio of MCCs identified in the accreting phase of \flower with different $n_{\rm cut}$. The most massive structures
identified with a low $f_{\rm gas}$ correspond to the molecular disk/arms of \flower (see also \Fig{vv}).
%
Thus, these structures encompass a large amount of stellar mass that is already assembled in \flower. These disk/arm structures are excluded 
in the discussion of MCC dynamics in the remainder of this paper. 
\label{fig:stellarRatio16}}
\end{figure}

The most massive structures ($M_{\rm gas}>$10$^7$\,\Msun) correspond
to the molecular disk of the galaxy (see e.g., \Fig{MCC}), which is
identified as a single component at low $n_{\rm cut}$. This main disk
component
% mm2 occupy the top right   [left not right!]
          occupies the top left
corner of \Fig{stellarRatio16}, with a low gas mass fraction of
$f_{\rm gas}< 5\%$. The velocity dispersion of such a structure is
dominated by bulk
% mm2 motions,
rotational motion,
as shown in \Fig{vv}, where we compare the velocity dispersions of MCCs resulting from bulk ($\sigma_{\rm bulk}$) versus non-thermal turbulent motions ($\sigma_{\rm NT}$) in the accreting and quiescent phases of \flower. The accreting phase of \flower displays a disturbed morphology, whereas the quiescent phase displays a disk-like morphology (\Fig{MCC}).
%
Excluding the structure corresponding to the molecular disk, the
velocity dispersions of most MCCs in the accreting phase of \flower
are dominated by turbulent motions, 
% mm2 . On the other hand, [the first hand is missing]
  while  in the quiescent disk-like phase, $\sigma_{\rm bulk}$ is at
  least comparable to $\sigma_{\rm NT}$ for almost half the MCCs.
%mm2 in the quiescent disk-like phase.
%
For these reasons, the most massive MCCs are excluded in the discussion of the dynamics (\Sec{diss}), as they are dominated by large-scale shear; however, we include them in the scaling relation plots (\Fig{larsons_single} and \Fig{alpha16-28}), as would be done for an observational study.

@@

\begin{figure}
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss16-28-veldisp.pdf}
\caption{Gas velocity dispersions resulting from bulk versus turbulent motions for molecular structures 
identified across all values of $n_{\rm cut}$, shown using the same color-coding as \Fig{stellarRatio16}.
%
Top and bottom panels show structures identified in the accreting phase and the quiescent phase, respectively.
The accreting phase of \flower displays a more disturbed morphology compared to the quiescent phase, which displays a disk-like morphology (see \Fig{MCC}).
%
The dashed black lines show a one-to-one mapping between the axes to facilitate comparison. 
%
Velocity dispersion from turbulent motions dominates over bulk motions for MCCs in the accreting phase, whereas 
$\sigma_{\rm bulk}$ is comparable to $\sigma_{\rm NT}$ for some MCCs in the quiescent disk-like phase.
\label{fig:vv}}
\vspace{0.5em}
\end{figure}

@@

\begin{figure*}
\centering
\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/3by2_clumpProp_ss16-ss22.png}
\caption{
Linewidth-size relation (top), $\alpha_{\rm vir}$-mass relation
(middle), and $\sigma_{\rm gas}^2/R$-$\Sigma_{\rm gas}$ relation (bottom) for
MCCs (star symbols) identified in the two most extreme evolutionary
stages of \flower---accreting (left) and starburst (right). Star symbols are color-coded by density threshold
$n_{\rm cut}$, as illustrated by the colorbar shown on the right.
Gas-only $\alpha_{\rm vir}$ (orange star symbols) is overplotted, and is of the same order of magnitude as $\alpha_{\rm vir, tot}$ for most MCCs
since they are gas-dominated (see \Fig{stellarRatio16}) \AP{I think the orange points makes the figure more messy, an alternative would to remove them and discuss the point in the text}. 
Stability of the biggest structures is strongly influenced by the stellar component, given their low $f_{\rm gas}$ (see \Fig{stellarRatio16} and \Sec{dist}).
The gray dotted lines shown in the bottom panels correspond to the various annotated external pressures needed in order for
the gas to be in equilibrium, see Equation~\ref{eqn:v0}.
Literature data are taken from \citet{Larson81a, Heyer04a, Rosolowsky05a, Bolatto08a, 
  Swinbank11a, Leroy15a, Kauffmann17a},
% mm2
    and \citet{Kauffmann17b}.
% black dot = extragalactic GMCs in quiescent environments
MCCs in the starburst phrase have lower $\alpha_{\rm vir}$ than in the accreting phase.
%mm2 [this was dangling here.  I moved it up to the citation list.] and \citet{Kauffmann17b}.
\label{fig:larsons_single}}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[trim=0 0 0 0, clip, width=1.05\textwidth]{\figpath/3by2_clumpProp_allss}
\caption{Same as \Fig{larsons_single}, except star symbols are showing
  molecular gas structures identified across all evolutionary stages
  traced in our simulation,
  color-coded by the SFR of \flower in those stages (see colorbar on the right). Left panels show structures identified using a low density threshold of $n_{\rm cut}$\eq0.53\,\cc and the right panels show those identified using a high density threshold of $n_{\rm cut}$\eq18.96\,\cc.
The biggest MCCs identified at the low density threshold, occupying the top right corner of the top left panel, correspond to the molecular 
disk and arms of \flower, and are broken down into smaller MCCs at higher density thresholds (see top right panel). 
Notably fewer MCCs populate the right panels because there are only a few MCCs with neighboring cells reaching high H$_2$ densities of $n_{\rm cut}\simeq$19\,\cc.
The high velocity dispersion in \flower is largely driven by non-thermal pressure (see \Fig{vv}).
\label{fig:alpha16-28}}
\end{figure*}

Here, we focus on the MCC properties in the two most extreme evolutionary stages of \flower---the accreting and starburst phases (see \Sec{sfh}). 
These properties are plotted in \Fig{larsons_single} together with observational results of nearby and $z$\,$\simeq$2 molecular structures for comparison.

During the accreting phase, MCCs in \flower\ are characterized by
large velocity dispersions ($\sigma \simeq 100 \mbox{ km s}^{-1}$) and sizes ($R\simeq 100$\,pc). These values are comparable to those found in starburst galaxies, such as the nearby gas-rich galaxy M64 and the $z$\ssim2 starbursting disk galaxy SMM\,J2135-0102 \citep{Rosolowsky05a, Swinbank11a}, but are higher than those found in the Milky Way and extragalactic GMCs by an order of magnitude \citep{Heyer04a, Bolatto08a}.

% middle
While the virial parameter defined as Equation~\ref{eqn:alpha} is typically used in observational studies, as they are designed to probe structures that are composed of mainly molecular gas only, we calculate the virial parameter of MCCs including the influence from the stellar component (i.e., $\alpha_{\rm vir, tot}$ via Equation~\ref{eqn:alpha_tot}) given the high stellar-to-gas mass ratios of some molecular structures identified (see \Fig{stellarRatio16}).
% 
The biggest MCC identified at low $n_{\rm cut}$ and with the highest stellar-to-gas mass ratio ($\gtrsim$\,1; \Fig{stellarRatio16}) corresponds to the central main 
disk of \flower (see top panels of \Fig{MCC} and \Sec{distribution}). The large amount of stellar mass already assembled in \flower
explains the low {\em total} virial parameter seen in the middle left panel of \Fig{larsons_single}, where the stellar gravitational potential 
influences the overall stability. On the other hand, the MCCs in this phase are mostly stable, with 
virial parameter comparable to some of the molecular structures
observed in the Milky Way,
% mm2 but the former is
     though the MCCs are
     more massive.

@@

%mm2 [fiddled with tenses and plurals]
If constant column density (Larson's third relation) were truly a
fundamental property of molecular clouds,
% or the roughly linear relationship between $\rho$ and $R$ of MCCs.
% mm2 (i.e., 
   and if virial equilibrium were a universal property of molecular clouds with negligible surface pressure, 
one would expect a single point in the $\sigma_{\rm
  gas}^2/R$--$\Sigma$ relation at
% mm a given gas
    that
mass surface density $\Sigma$. 
The variation in $\sigma_{\rm gas}^2/R$ with $\Sigma$ seen here suggests that column density is not a fundamental property of 
molecular clouds
% mm2 [maybe this is excessive, but if we are discussing the issue it
% seems worth citing.]
     in agreement with \citet{Heyer09a}.
Previous studies suggest that the observed mass-size relation of molecular clouds 
is solely a result of $\rho\propto M R^{-3}$ and may be an artifact of the limited range of 
column densities a specific molecular line tracer is sensitive to \citep[see e.g.,][]{Ballesteros02a, Ballesteros11a}.
%For instance, \citet{Ballesteros02a} show that the density
%of clouds ($\rho$) is independent of their size ($R$) when one properly extract these quantities in three-dimensional space instead of
%two-dimensional space; the latter is done in \obs.
%When they project the clouds into two-dimensional space and measure the densities and sizes of clouds for a given
%line tracer, they find $\rho \propto R^{-1}$, which is unsurprising since $N_H$ is just a constant.
%They therefore argue that the mass-size relation is simply a result of $\rho\propto M R^{-3}$
%observed in 2D-space at a fixed column density (cf. an actual physical relation of $M \propto R^{4/3}$ claimed in
%observational studies). % where $\rho$ would be proportional to $R^{-1/2}$
%% since $M$ would then scale as $R^{3}$ (ånd naturally display a linear relationship in $\log M - \log R$ plot).

@@

% Starburst
In the starburst phase, MCCs have velocity dispersion and sizes similar to those in the accreting phase; however, 
MCCs in the starburst phase span a wider range in gas surface density 
(bottom panels of \Fig{larsons_single}) and have lower virial parameters.
That is, MCCs in the starburst phase are more susceptible to collapse, as expected.
The gas surface density of MCCs in both accreting and starburst phases is higher than that in the solar neighborhood
of the Milky Way and the Large Magellanic Cloud (LMC), but comparable to those observed in starburst galaxies and the nearby 
ultra-luminous IR galaxies \citep[ULIRGS;][]{Boulares90a, Scoville91a, Weiss01a, Hughes10a, Leroy15a}.
% LMC: 0.01 g cm^-2
% M82: 0.1 g cm^-2
% Arp 220: 7-20 g cm^-2
%
% Due to a time delay between cloud collapse and \SF, we also compare the virial parameter of MCCs in the pre-starburst phase and post-starburst phase.
%\Fig{alphaEvol} shows that most MCCs in the pre-starburst phase have even lower virial parameter than in the starburst phase. On the other hand,
%the virial parameter of MCCs in the post-starburst phase is higher than in both the pre-starburst and the starburst phase.
%This is consistent with our physical intuition of gas instability leading to \SF.
